Locally-Oriented Programming: A stunningly simple programming model for GPU programming in Fortran and C++

### 2012-05-30 papers/LOPe/programming-model.tex
Added a paragraph on memory management.

>>>>

%% A note from a conversation with Matt regarding memory management
%%
\subsection{Memory Management}

The Fortran language has much tighter restrictions on aliasing than does C.
So unless a variable has the pointer or target attribute, it cannot be aliased.
Thus the compiler is able to agressively optimized for memory movement between
the CPU and accelerator.  However, because the design philosophy of coarrays
is that memory transfer between images can be expensive, the programmer must
explicitly transfer memory between images with explicit syntax with square
bracket notation, i.e., $a[1] = a[2]$.  So we allow the compiler to manage
memory within an image but require the use of {\tt halo_exchange} for the
transfer of halo memory between images.
